Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
tuner network combined with reducer network

 See \textbf{Figure 1} for an example of a Reducer Network. \note{Desai: Make figure 1}.

\subsection{Tuners}
\note{Desai: can you write this section, I don't know the details}
\subsection{Tuning the Reducer Network}

\subsection{Tuner Network}
\note{Desai: also this section :) }

>>>>

 See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.

\begin{figure}[h]
\includegraphics[scale=0.3]{figure/redNetwork.pdf}
\caption{An Reducer Network we used to produce one of our results.
The input shape is sliced into two layers with the stratum partition node.
The top slice is then partitioned into columns. Each column is assigned
a stack of material layers.}
\label{fig:red1}
\end{figure}

\subsection{Tuners}
Tuner is an interface between a Reducer Node and an optimization algorithm.
A Tuner contains a pointer to a Reducer Node and a pointer to a generic optimization subroutine.
When a Tuner is linked to a Reducer Node, 
it can tune the free variables contained in the sub-tree rooted at that node.
\note{Desai: can you write this section, I don't know the details}
\subsection{Tuning the Reducer Network}
A Tuner initializes the optimization by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables.
The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables.
With the search space specifies, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine.
\subsection{Tuner Network}
\note{Desai: also this section :) }
For some fabrication problems, the best material to assign to a location
depends on the material assignment at nearby locations. 
Tuning the free variables as if they were independent usually yields
unsatisfactory results.
Therefore, we allow the tuner to share information according to 
a user-specified graph structure. 
This allows our framework to be interfaced with a wide range of existing
graph based optimization and inference algorithms.
For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right). 
The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}.
The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}.
A simplified view of the combined graph is shown in Figure~\ref{fig:combine}.
Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.

\begin{figure}[h]
\includegraphics[scale=0.3]{figure/tuner.pdf}
\caption{A sample Tuner Graph for the Floyd–Steinberg dithering algorithm.}
\label{fig:tuner}
\end{figure}

\begin{figure}[h]
\includegraphics[scale=0.3]{figure/netAndTuner.pdf}
\caption{Combined graph for the error diffusion example.}
\label{fig:combine}
\end{figure}
